\documentclass[10pt,oneside]{article} 
\usepackage{fullpage}
\usepackage[paper=letterpaper]{geometry} 
\textheight=10.0in
\pagestyle{empty} 
\raggedbottom 
% \usepackage{minion}

\usepackage{tgpagella}
% \usepackage{venturis2}
\usepackage[T1]{fontenc}

%\addtolength{\topmargin }{-30pt}
%\addtolength{\textheight}{10pt} 
\newcommand{\name}{Amita Ekbote}
\newcommand{\addr}{San Francisco Bay Area, CA}
\newcommand{\phone}{312$-$330$-$8641}
\newcommand{\email}{amita.ekbote@gmail.com}
\newcommand{\bigname}[1]{\begin{center}\Huge\scshape#1\end{center}}
\newcommand{\subheader}[1]{\textsc{\textbf{\large{#1}}}}
\renewcommand{\labelitemi}{}
\renewcommand{\labelitemii}{$\circ$}

\geometry{letterpaper,tmargin=0.5in,bmargin=1in,lmargin=0.7in,rmargin=0.7in,headheight=0in,headsep=0in,footskip=.0in}

\begin{document}
\bigname{\name}
{\small \addr; Ph: \phone\hfill\email}
\vspace{0pt}
\rule[3mm]{\textwidth}{1pt}

\vspace{-10 pt}
%{\flushleft {\large \textbf{Objective}}}
%\vspace{-5 pt}
%	\begin{itemize}
%		\item  Seeking a full-time position in an industry leading human-computer interaction research lab.
%	\end{itemize}



%{\flushleft{\large \textbf{Research Interests}}}
  
%  \begin{itemize}
%   \item Multitouch and Multimodal Interaction Design, Gesture Recognition, Human-Computer Interaction, Information Semantics and Information Visualization.
%  \end{itemize}

{\flushleft{\large \textbf{Summary}}}

%% Seeking a challenging full time position in systems software where my skill set is valued, while giving me an opportunity to explore.

  \begin{itemize}
    %\setlength\itemsep{-3 pt}
    \item \textbf{Experience:} Worked with distributed systems at scale in the Compute team at Netflix.
    \item \textbf{Interests:} Distributed Systems, Platforms and OS
  \end{itemize}




{\flushleft{\large \textbf{Work Experience}}}
\begin{itemize}
      \item
      \subheader{Netflix}, Los Gatos, CA\hfill July 2018 $-$ Present\\
      Sr Software Engineer, Titus team(Container platform)
      \vspace{-4 pt}
      \begin{itemize}
        \item Work on building and maintaining the container platform using mesos on Amazon EC2.
        \item Work on docker registry. 
      \end{itemize}
  
      \item
      \subheader{Mesosphere}, San Francisco, CA\hfill Sept 2016 $-$ July 2018\\
      Software Developer, Cluster operations
      \vspace{-4 pt}
      \begin{itemize}
        \item Worked on making container orchestration cluster upgrades seamless.
	\item Worked on building DC/OS(Mesos) services such as cluster and node checks and dcos licensing.
        \item Contributing to open source everyday, https://github.com/amitaekbote.
      \end{itemize}
      
    \item	
      \subheader{Amazon Web Services}, Cupertino, CA\hfill Aug 2013 $-$ Present\\
      Software Developer, EC2
      \vspace{-4 pt}
      \begin{itemize}
        \item Added support for new linux kernels for the EC2 VM Import/Export service.
        \item Expand the service to newer regions and automate deployments.
		\item Lead the effort to reduce operations pain and focus on providing a better customer experience.
        \item Specialized in debugging customer images which failed on boot.
        \item Worked with the kernel and operating systems team on next generation EC2 architecture. 
      \end{itemize} 

    \item
      \subheader{Cisco Systems Inc}, San Jose, CA\hfill Jul 2010 $-$ Aug 2013\\
      Software Developer
      \vspace{-4 pt}
      \begin{itemize}
        \item Added mux buffers to linecards, for multiplexing traffic between redundant supervisors.
        \item Augmented Cisco IOS for linecard bringup on the Catalyst 4500\textsuperscript{\textregistered} 32 port switch.
        \item Bringup and traffic testing of VSS (Virtual Switching System) on single supervisor switches,
        \item Integrated PCIe OIR (Online Insertion and Removal) for a linecard.
        \item Troubleshooting process and interrupt handling for Cisco switches.
      \end{itemize} 

    \item
      \subheader{BITS Networked Systems Laboratory}, Chicago, IL\hfill May 2009 $-$ May 2010\\
      Research Assistant, University of Illinois at Chicago 
      Mentor: Dr. Jacob Eriksson
      \vspace{-4 pt}
	    \begin{itemize}
        \item Optimized long range wireless throughput by developing a new rate adaptation algorithm.
        \item Thesis was developed while working on the project \emph{Xenonets:Networks of cooperating strangers}.
        \item Click Modular router installation and traffic testing using Ubiquiti routers with openwrt firmware. (C++)
      \end{itemize}  

    \item
      \subheader{National Center for Data Mining}, Chicago, IL\hfill Aug 2008 $-$ Aug 2009
      Research Assistant, University of Illinois at Chicago 
      Mentor: Dr. David Hanley
      \vspace{-4 pt}
      \begin{itemize}
        \item Developed modules for Cistrack system, a lightweight laboratory information management system (LIMS).
      \end{itemize}

    \item
      \subheader{Motorola}, Schlaumburg, IL\hfill May 2008 $-$ Aug 2008\\
      Summer Intern
      \vspace{-4 pt}
      \begin{itemize}
  	    \item Implemented the AV standards version 3 for UPNP protocol, used for DLNA in set top boxes.
      \end{itemize}
  \end{itemize}

{\flushleft {\large \textbf{Education}}}
  \begin{itemize}
  \item 
    \subheader{University of Illinois at Chicago}, Chicago, IL\hfill Aug 2007 $-$ May 2010\\
    M. S. in Computer Science.\\
    Master's Thesis: Asymmetry Aware Rate Adaptation (AARA) algorithm .\\
    Advisor: Dr. Jacob Eriksson.
  \item
    \subheader{CBIT, Osmania University}, Hyderabad, India\hfill Aug 2003 $-$ May 2007\\
    Bachelor of Technology, Computer Science and Engineering.
  \end{itemize}
%\vspace{6 pt}


%% {\flushleft {\large \textbf{Skills}}}
%%   \begin{itemize}
%%     \item \textbf{Languages:} C, C$++$, Ruby\textit{[Expert]}
%%     \item \textbf{Developer Essentials:} Emacs, Vim, Git, Shell. \textit{[Proficient]} 
%%   \end{itemize}
%\vspace{6 pt}


%{\flushleft {\large \textbf{Projects}}}
%\begin{condensed_items}
%\item Keyword based categorization of Research Articles.
%\item Supporting citation chaining through metadata extraction and visualization of research articles from the ACM Portal.
%\end{condensed_items}
%\vspace{6 pt}

{\flushleft {\large \textbf{Professional Activities}}
  \begin{itemize}
    \item Volunteered with the organization of Amazon Women in Engineering for Grace Hopper Conference 2014.
    \item Volunteered at March of dimes, Habitat for Humanity, and Turning wheels for kids.
  \end{itemize}


\center{\textit{References available upon request.}}

\end{document}
